Group meetings

### 2023-09-20 diapo/23-09-23_meeting/main.tex
changed date for last weeks missed pres...
Ready for vendredi, ca rime

\date{26/05/2023}

@@

  \begin{frame}
    \frametitle{Problems/doubts}
    \begin{itemize}
      \item What is the approximate onChip area of an opAmp
      \item What is the precision of a memristor when setting the resistance
      \item I feel like my state of the art is missing content...
      \item When would my thesis defense happen ?
      \item I'm afriad i might not have time to finish on time wiht enough content.
    \end{itemize}
  \end{frame}

>>>>

\date{23/09/2023}

@@

  \begin{frame}
    \frametitle{Problems/doubts}
    \begin{itemize}
      \item What is the approximate onChip area of an opAmp ?
      \item What is the approximate onChip area of an resistor ?
      \item What is the precision of a memristor when setting the resistance ?
      \item I feel like my state of the art is missing content...
      \item When would my thesis defense happen ?
      \item Is a demo of simple system useful ?
    \end{itemize}
  \end{frame}
